\documentclass[12pt]{article}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=1in}

\title{Hello Hamilton: Progress Log and Roadmap}
\date{}
\begin{document}
\maketitle

\section*{1. Completed Milestones}

\subsection*{Day 1--2}
\begin{itemize}[leftmargin=*]
    \item Project created with clear architecture vision.
    \item Frontend scaffolded using React + Vite.
    \item Leaflet map successfully rendered.
    \item Backend Express server created.
    \item Event route (\texttt{/events}) returning hardcoded JSON.
    \item Frontend fetching events from backend.
    \item Map markers placed using event coordinates.
    \item Basic category filter implemented.
    \item Full event schema finalized.
\end{itemize}

\section*{2. Current Focus (Day 3)}
\begin{itemize}[leftmargin=*]
    \item Build full multi-filter panel.
    \item Create scalable filter state system.
    \item Implement UI for all filters.
    \item Combine filters into unified logic.
\end{itemize}

\section*{3. Near-Term Objectives (Day 4--6)}
\begin{itemize}[leftmargin=*]
    \item Install Prisma.
    \item Configure PostgreSQL connection.
    \item Create Prisma schema matching event model.
    \item Migrate and seed database.
    \item Replace static JSON with DB queries.
    \item Move filtering logic optionally to backend.
\end{itemize}

\section*{4. Longer-Term Objectives}
\begin{itemize}[leftmargin=*]
    \item Search bar for event names.
    \item "Events near me" geolocation support.
    \item Dedicated event cards + list view.
    \item User-submitted events.
    \item Admin panel with event editing tools.
    \item Daily automatic updates from public feeds.
    \item Optional: AI-assisted extraction for event details.
\end{itemize}

\section*{5. Nice-to-Haves}
\begin{itemize}[leftmargin=*]
    \item Dark mode polish.
    \item Category icons.
    \item Simple animations on map interactions.
    \item Public API endpoint for other Hamilton devs.
\end{itemize}

\end{document}
