\documentclass[12pt]{article}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=1in}

\title{Hello Hamilton: Requirements Document}
\date{}
\begin{document}
\maketitle

\section*{1. Project Overview}
Hello Hamilton is a map-based event and attraction viewer for Hamilton, Ontario. 
It displays both upcoming events and permanent attractions using a React + Vite frontend and an Express backend. 
A PostgreSQL database with Prisma ORM will be integrated later.

\section*{2. High-Level Goals}
\begin{itemize}[leftmargin=*]
    \item Provide a clean map interface for discovering local events and attractions.
    \item Allow users to apply multiple filters simultaneously.
    \item Support scalable event data from various sources.
    \item Organize experiences for both locals and newcomers.
\end{itemize}

\section*{3. Functional Requirements}

\subsection*{3.1 Frontend}
\begin{itemize}[leftmargin=*]
    \item Render an interactive Leaflet map.
    \item Fetch event data from backend API.
    \item Display event markers with popups.
    \item Provide filtering UI:
    \begin{itemize}
        \item Category
        \item Cost
        \item Indoor/Outdoor
        \item Energy Level
        \item Seasonal
        \item Group Size
    \end{itemize}
    \item Apply combined filters and update visible markers.
\end{itemize}

\subsection*{3.2 Backend}
\begin{itemize}[leftmargin=*]
    \item Serve event data at \texttt{/events}.
    \item Provide CORS-safe responses for local development.
    \item Validate event schema (manual now, Prisma later).
    \item Prepare for future database integration.
\end{itemize}

\subsection*{3.3 Future Database Layer}
\begin{itemize}[leftmargin=*]
    \item A Prisma schema representing the finalized event structure.
    \item PostgreSQL database with seeded events.
    \item Replace static event JSON with DB queries.
    \item Enable real-time filtering on server side for large datasets.
\end{itemize}

\section*{4. Non-Functional Requirements}
\begin{itemize}[leftmargin=*]
    \item Clean, minimal UI usable on desktop and mobile.
    \item Maintainable code structure:
    \begin{itemize}
        \item Clear component hierarchy
        \item Centralized filter state
    \end{itemize}
    \item Future-proofing for integrations:
    \begin{itemize}
        \item Automated data ingestion
        \item AI-based autofill of event fields
    \end{itemize}
\end{itemize}

\section*{5. Constraints}
\begin{itemize}[leftmargin=*]
    \item No database or ORM integration until Day 4+.
    \item Limited initial dataset (manual JSON).
    \item Prioritize clarity and incremental progress.
\end{itemize}

\end{document}